%Section Template
\documentclass[../main.tex]{subfiles}

\begin{document}
	

	\section*{}
	Q. Which scriptures most clearly prophesy of Christ?
	
	A. The Lord will raise up a prophet among you, and you will listen to him just as you listen to the Lord. [Deut. 18:15]\qVerse{Deuteronomy}{18}{15}
	
	The Lord will give you a sign: A virgin will conceive and bear a son, and shall name Him Immanuel. [Isaiah 7:14]\qVerse{Isaiah}{7}{14}
	
	Q. Didn't Christ exist before becoming flesh? What Scriptures proves this against people who wrongly claim otherwise?
	
	The little town of Bethlehem will bring forth a ruler in Israel who has existed since ancient times. [Mic. 5:2]\qVerse{Micah}{5}{2}
	
	Jesus said to them, "Truly I tell you, I existed before Abraham." [John 8:58]\qVerse{John}{8}{58}
	
	Now, Father, glorify me through You, with the same glory I had before the world existed. [John 17:5]\qVerse{John}{17}{5}
	
	And to make men see the fellowship of the mystery, which was in God, who created all things through Christ, since the beginning of the world. [Eph. 3:9]\qVerse{Ephesians}{3}{9}
	
	He created everything in Heaven and Earth, visible and invisible, be they kings, nations, or governments. They were created by Him and for Him. [Col. 1:16]\qVerse{Colossians}{1}{16}
	
	God has in these last days spoken to us through His son, who He has appointed heir of all things, and through whom he made the worlds. [Heb. 1:2]\qVerse{Hebrews}{1}{2}
	
	Q. Those verses make it clear that the world was created by Christ, but what Scriptures prove Christ's divinity against people who claim He isn't divine?
	
	A. The Word was God. [John 1:1]\qVerse{John}{1}{1}
	
	Israel's ancestors are the ancestors of Christ, who is God over all, forever blessed, amen. [Rom. 9:5]\qVerse{Romans}{9}{5}
	
	Christ, being equal with God, did not exploit his equality with God. [Phil 2:6]\qVerse{Philippians}{2}{6}
	
	We know the Son of God has come, and has given us the understanding to know the true God. We are in the true God through his son Jesus Christ: This is the true God and eternal life. [1 John 5:20]\qVerse{IJohn}{1}{20}
	
	Q. What glorious names does Scripture give unto Jesus Christ, the eternal son of God?
	
	A. His name will be called Wonderful, Counselor, the Mighty God, the Everlasting Father, the Prince of Peach. [Isa. 9:6]\qVerse{Isaiah}{9}{6}
	
	He is the image of the invisible God, the first-born of every creature. [Col 1:15]\qVerse{Colossians}{1}{15}
	
	He is the brightness of God's glory and the image of God's person (or as the Greek states, His substance). [Heb. 1:3]\qVerse{Hebrews}{1}{3}
	
	He wore a blood-dipped robe, and His name was the Word of God. [Rev. 19:13]\qVerse{RevelationofJohn}{19}{13}
	
	Q. How does Scripture describe the birth of Christ?
	
	A. This is how Christ was born: When Mary was engaged to Joseph (but before they were married), she became pregnant with the child of the Holy Spirit. [Matt. 1:18]\qVerse{Matthew}{1}{18}
	
	The angel said to Mary, "Fear not, for God favors you. You will have a son and name him Jesus. He will be great, and called the Son of the Highest, and God shall give him David's throne." Mary said to the angel, "How can I have a son, since I'm a virgin?" The angel answered, "The Holy Spirit will come to you, and the power of God will overshadow you. The child you bear will thus be called the Son of God. [Luke 1:30-32, 34-35]\qRange{Luke}{1}{30}{32}\textsuperscript{,}\qRange{Luke}{1}{34}{35}
	
	
	
	
	
	
	
	
	
	
	
	
\end{document}