% barclay-catechism/main.tex
\input{../../templates/template.tex}
\input{../../bible/KJV.tex}

\title{Barclay's Catechism: Thought for Thought}
\author{Robert Barclay, various translators}

\begin{document}
	
	\maketitle

	A catechism and confession of faith which is in agreement with the beliefs of the apostles and church fathers (most importantly Christ himself). This catechism outlines the principles and doctrines believed by the Christian churches of Great Britain and Ireland, mockingly called "Quakers". Despite the mockery and scorn heaped upon them, their beliefs align with those of the original Christian church and the saints. This is evident by the words of the Bible itself. This catechism provides references to these Scriptures through a series of important, yet easily answered, questions. These answers should satisfy the concerns and curiosities of everyone, whether they are educated or not.
	
	Also included is an explanation of our disagreements with, and an appeal to, others who call themselves Christians.
	
	\textit{Search the Scriptures (or, ye search the Scriptures) for in them ye think ye have Eternal Life, and they are they which testifie of me; But ye will not come to me that ye might have life.} John 5:39-40
	
	\tableofcontents
	
	\subfile{00-preface/chapter_main.tex}
	\subfile{01-god/chapter_main.tex}
	\subfile{02-rule/chapter_main.tex}
	\subfile{03-manifest/chapter_main.tex}
	\subfile{04-birth/chapter_main.tex}
	\subfile{05-light/chapter_main.tex}
	\subfile{06-justification/chapter_main.tex}
	\subfile{07-perfection/chapter_main.tex}
	\subfile{08-perseverance/chapter_main.tex}
	\subfile{09-church/chapter_main.tex}
	\subfile{10-worship/chapter_main.tex}
	\subfile{11-sacraments/chapter_main.tex}
	\subfile{12-life/chapter_main.tex}
	\subfile{13-magistracy/chapter_main.tex}
	\subfile{14-resurrection/chapter_main.tex}
	\subfile{15-intro/chapter_main.tex}
	\subfile{16-confession/chapter_main.tex}

	% Add more chapters as needed

\end{document}
