%Barclay's Catechism Preface - Letter to the Reader
\documentclass[chapterpreface_main.tex]{subfiles}

\begin{document}
	

	\section{Letter to the Reader}
	Since Christians first began to deviate from the pure simplicity of the Gospel (which happened even in the times of the Apostles), countless made-up notions and traditions have been devised by men which have hindered the Christian faith. First, they were added to the Gospel, then they were considered equally important to the Gospel. Eventually they came to surpass the Gospel to these men, shutting the Gospel's truth out entirely. The Gospel was thus replaced with something that called itself Christianity but lacked the true substance of Christianity altogether. Even so, God saw fit to raise up true witnesses for Himself in every age and generation. These witnesses received revelation from God that allowed them to testify, to varying extents, against the superstitions and apostasies of their time. Particularly because of the Light of God inspiring the Protestant Reformation about 150 years ago, which then spread to many nations, Satan received a deadly wound, as many Christians protested against and left the Roman Catholic Church because of their false doctrines and their many superstitious church traditions. Unfortunately, instead of continuing the righteous work of their predecessors, the successors of these Protestants are committing the same errors that the original Protestant Reformers sought to do away with.
	
	Most Protestants share a disagreement with the Roman Catholic Church in two regards (though they disagree with each other on most other things):
	
	First, that the doctrines of the Christian faith are founded upon the Bible, and any principles or doctrines with contradict or even just absent from the Bible are Antichristian and should be avoided.
	
	Second, that the Bible is easy to understand, and therefore every Christian and church member should read it for themselves so they can better understand their own faith. They should read the Bible for this purpose, not because their own imperfect church told them to do so.
	
	Despite holding these beliefs, modern-day Protestants are persecuting people who disagree with them and hold to the Bible instead of unbiblical traditions, just like the Catholics did to the early Reformers. This will be demonstrated in a later chapter.
	
	They are comparable to the old scribes and pharisees, who celebrated Moses and the prophets, and called themselves children of Abraham, but were the greatest opponents of Christ, even though Moses and the prophets themselves testified of Christ's coming. These scribes and pharisees accused Christ of law-breaking and blasphemy.
	
	The behavior of those scribes and pharisees can be seen today, as there is now a persecuted and hated group of people who are accused of heresy by people who claim to follow the Bible. However, these people's beliefs are found word-by-word in the Bible itself, even though they are accused of violating and denying the Bible in favor of their own beliefs.
	
	This catechism and confession of faith is intended to disprove the accusations against these people. If you love the Bible and claim to follow its doctrines instead of man-made beliefs and tradition, you'll easily see that the beliefs of these so-called "Quakers" are plainly found in the Bible, without adding anything unbiblical to them. In fact, in those accusations hurled at them by their persecutors (blinded by the ungodly wisdom of the world), the Bible most plainly sides with the Quakers.
	
	In the answers to the questions I present, every word of my answer is founded in Scripture; if I include my own interpretations of the words, it is only to lead into the next question, not to impart my own reasoning to the reader. If you're not blinded by your own biases, then you can decided for yourself whether the Scriptures I provide truly answer the questions presented.
	
	I had the idea of writing this catechism and confession shortly after God opened my eyes to true Christianity, and after further Bible study, I have found time to accomplish it.
	
	This work could be further extended with many more citations from Scripture, but my memory is limited. Even so, I thank God for His Spirit's help, as his Spirit has a much better memory than me. That same Spirit will help the serious reader of this work to discover its truth, and will give assurance to the true believer. I desire and pray for this daily.
	
	By Robert Barclay, a servant of the Christian church, from Urie in my native country of Scotland, on June 11, 1673.\footnote{Editor: The original work avoided the use of the name of the month, which has a pagan origin, instead calling it "sixth month".}
	
	

\end{document}