%Barclay's Catechism Preface - Letter to the Reader
\documentclass[../main.tex]{subfiles}

\begin{document}
	

	\section*{}
	Q. Seeing as most Christians agree that the greatest happiness is found in Eternal Life, what does Christ have to say about this Eternal Life?
	
	A. Eternal Life is given so that we can know God and Christ [John 17:3].\qVerse{John}{17}{3}
	
	Q. How does God reveal this knowledge?
	
	A. The same God who commanded Light to shine out of darkness has also shined in our hearts, to give us the Light of knowing God's glory through the face of Jesus Christ [2 Cor. 4:6]. \qVerse{IICorinthians}{4}{6}
	
	Q. How many Gods are there?
	
	A. One God [Eph. 4:6]. \qVerse{Ephesians}{4}{6}
	
	We know that idols are powerless and there is no god but the one God, so for us there is only one God.[I Cor. 8:4,6]\qVerse{ICorinthians}{8}{4} \qVerse{ICorinthians}{8}{6}
	
	Q. What is God?
	
	A. God is a spirit [John 4:24]. \qVerse{John}{4}{24}
	
	Q. Of all the good things that can be said about God (as noted in Scripture), which is the most important, because it is the message that the Apostles took special care to record?
	
	A. This the message we heard from him and tell to you: God is Light, and there is no darkness in Him [1 John 1:5].\qVerse{IJohn}{1}{5}
	
	Q. Who bears witness in heaven?
	
	A. The Father, the Word, and the Holy Spirit bear witness in heaven, and these three are one [1 John 5:7].\qVerse{IJohn}{5}{7}
	
	Q. How does Christ say that we can know God?
	
	A. All things come to me from my Father; and no man knows the Son of God but the Father; and no one knows the Father but the Son and anyone the the Son reveals Him to [Luke 10:22; Matt. 11:27].\qVerse{Luke}{10}{22}\qVerse{Matthew}{11}{27}
	
	Jesus says He is the Way, the Truth, and the Life, and no one goes to the Father but through Him [John 14:6].\qVerse{John}{14}{6}
	
	Q. How does the Son reveal the knowledge of God?
	
	A. As the Bible states, we can't experience the things God has prepared for those that love him, except through His Spirit. The Spirit understands God. After all, only a man's spirit can understand the man. Likewise, only God's Spirit can truly understand God. Now, God has given us His Spirit so that we can know what God has given us [1. Cor. 2:9-12].\qRange{ICorinthians}{2}{9}{12}
	
	Christ tells us that the Holy Spirit, who the Father will send in Christ's name, will teach us and remind us of the things of God [John 14:26].\qVerse{John}{14}{26}

\end{document}