%Section Template
\documentclass[../main.tex]{subfiles}

\begin{document}
	

	\section*{}
	Q. Which scriptures most clearly prophesy of Christ?
	
	A. The Lord will raise up a prophet among you, and you will listen to him just as you listen to the Lord. [Deut. 18:15]\qVerse{Deuteronomy}{18}{15}
	
	The Lord will give you a sign: A virgin will conceive and bear a son, and shall name Him Immanuel. [Isaiah 7:14]\qVerse{Isaiah}{7}{14}
	
	Q. Didn't Christ exist before becoming flesh? What Scriptures proves this against people who wrongly claim otherwise?
	
	The little town of Bethlehem will bring forth a ruler in Israel who has existed since ancient times. [Mic. 5:2]\qVerse{Micah}{5}{2}
	
	Jesus said to them, "Truly I tell you, I existed before Abraham." [John 8:58]\qVerse{John}{8}{58}
	
	Now, Father, glorify me through You, with the same glory I had before the world existed. [John 17:5]\qVerse{John}{17}{5}
	
	And to make men see the fellowship of the mystery, which was in God, who created all things through Christ, since the beginning of the world. [Eph. 3:9]\qVerse{Ephesians}{3}{9}
	
	He created everything in Heaven and Earth, visible and invisible, be they kings, nations, or governments. They were created by Him and for Him. [Col. 1:16]\qVerse{Colossians}{1}{16}
	
	God has in these last days spoken to us through His son, who He has appointed heir of all things, and through whom he made the worlds. [Heb. 1:2]\qVerse{Hebrews}{1}{2}
	
	Q. Those verses make it clear that the world was created by Christ, but what Scriptures prove Christ's divinity against people who claim He isn't divine?
	
	A. The Word was God. [John 1:1]\qVerse{John}{1}{1}
	
	Israel's ancestors are the ancestors of Christ, who is God over all, forever blessed, amen. [Rom. 9:5]\qVerse{Romans}{9}{5}
	
	Christ, being equal with God, did not exploit his equality with God. [Phil 2:6]\qVerse{Philippians}{2}{6}
	
	We know the Son of God has come, and has given us the understanding to know the true God. We are in the true God through his son Jesus Christ: This is the true God and eternal life. [1 John 5:20]\qVerse{IJohn}{5}{20}
	
	Q. What glorious names does Scripture give unto Jesus Christ, the eternal son of God?
	
	A. His name will be called Wonderful, Counselor, the Mighty God, the Everlasting Father, the Prince of Peach. [Isa. 9:6]\qVerse{Isaiah}{9}{6}
	
	He is the image of the invisible God, the first-born of every creature. [Col 1:15]\qVerse{Colossians}{1}{15}
	
	He is the brightness of God's glory and the image of God's person (or as the Greek states, His substance). [Heb. 1:3]\qVerse{Hebrews}{1}{3}
	
	He wore a blood-dipped robe, and His name was the Word of God. [Rev. 19:13]\qVerse{RevelationofJohn}{19}{13}
	
	Q. How does Scripture describe the birth of Christ?
	
	A. This is how Christ was born: When Mary was engaged to Joseph (but before they were married), she became pregnant with the child of the Holy Spirit. [Matt. 1:18]\qVerse{Matthew}{1}{18}
	
	The angel said to Mary, "Fear not, for God favors you. You will have a son and name him Jesus. He will be great, and called the Son of the Highest, and God shall give him David's throne." Mary said to the angel, "How can I have a son, since I'm a virgin?" The angel answered, "The Holy Spirit will come to you, and the power of God will overshadow you. The child you bear will thus be called the Son of God. [Luke 1:30-32, 34-35]\qRange{Luke}{1}{30}{32}\textsuperscript{,}\qRange{Luke}{1}{34}{35}
	
	Q. Was Jesus Christ, son of the Virgin Mary, and ostensible son of Joseph, a real man?
	
A. Just as children are flesh and blood, so was Christ, so that His death could destroy the Devil. [Heb. 2:14]\qVerse{Hebrews}{2}{14}

Truely, he didn't take the nature of an angel, but instead took the lineage of Abraham, because he needed to be like his brethren, so that he could be a merciful and faithful high priest. [Heb. 2:16-17]\qRange{Hebrews}{2}{16}{17}

We don't have a high priest who can't empathize with our pain and weaknesses, but rather, He was tempted as we are, though He did not sin. [Heb. 4:15]\qVerse{Hebrews}{4}{15}

The gift of grace, by \textbf{one man}, Jesus Christ, has abounded unto many. [Rom. 5:15]\qVerse{Romans}{5}{15}

Now Christ has risen from the dead and become the first to resurrect, for since humanity caused death to come into the world, a human has also brought resurrection into the world. {1 Cor. 15:20-21}\qRange{ICorinthians}{15}{20}{21}

Q. How does Scripture describe the unity of Christ the Son of God with Christ the Man?

A. God's Word became flesh and lived among us (and we observed his glory, the glory of God's only Son) full of grace and truth. [John 1:14]\qVerse{John}{1}{14}

For the man sent by God speaks God's words, for God has given him the entirety of the Spirit. [John 3:34]\qVerse{John}{3}{34}

God anointed Jesus of Nazareth with the Holy Spirit and with power, so Jesus went about doing good and healing those afflicted by the Devil because God was with Him. [Acts 10:38]\qVerse{Acts}{10}{38}

It pleased God that the fullness of the Spirit dwelt in Christ. [Col. 1:19]\qVerse{Colossians}{1}{19}

In Christ dwells the fullness of God. [Col. 2:9]\qVerse{Colossians}{2}{9}

In Christ are hidden all the treasures of wisdom and knowledge. [Col. 2:3]\qVerse{Colossians}{2}{3}

Q. Why did Christ come to Earth?

A. Because God's law could not overcome the sinfulness of humanity, God sent His son as a human, resembling the sinful likeness of humanity, so that He could condemn sin as a man. [Rom. 8:3]\qVerse{Romans}{8}{3}

The Son of God came to destroy the works of the Devil. You know that He came to take away our sins. [1 John 3:8,5]\qVerse{IJohn}{3}{8}\textsuperscript{,}\qVerse{IJohn}{3}{5}

Q. Was Jesus Christ really crucified and resurrected?

A. My eyes have seen your salvation, which you have prepared before everyone, a light shining upon the Gentiles, and the glory of your people, Israel. [Luke 2:30-32]\qRange{Luke}{2}{30}{32}

God sent Christ as an atonement through faith in His blood, to declare his righteousness for the forgiveness of past sins, through the patience of God. [Rom. 3:25]\qVerse{Romans}{3}{25}

Walk in love as Christ loved us and gave Himself for us, a sweet-smelling offering and sacrifice to God. [Eph.5:2]\qVerse{Ephesians}{5}{2}

He brought peace through His blood on the cross, to reconcile everything unto Himself, be they in on Earth or in Heaven. You, who were sometimes the enemies of God through your wicked deeds, have been reconciled through his death, to make you holy and beyond reproach in the eyes of God. [Col. 1:20-22]\qRange{Colossians}{1}{20}{22}

Not by animal blood, but by His own blood, he entered the holy place, having obtained redemption for us. Thus the blood of Christ, who through the Holy Spirit offered his blameless self to God, clear your conscience of sin to serve God .[Heb. 9:12,14]\qVerse{Hebrews}{9}{12}\textsuperscript{,}\qVerse{Hebrews}{9}{14}

Christ suffered for sins, the just suffering for the unjust (to bring us to God), having been killed as a man, but strengthened by the Spirit. [1 Pet. 3:18]\qVerse{IPeter}{3}{18}

We see the Love of God in Christ giving His life for us. [1 John 3:16]\qVerse{IJohn}{3}{16}

Christ is the mediator of God's new testament, in that through His death to redeem sins under the first testament, those who are called can receive God's promised inheritance. [Heb. 9:15]\qVerse{Hebrews}{9}{15}

Q. So Christ is our mediator?

A. Christ is the lamb that was slain from the world's founding. [Rev. 5:12; 13:8]\qVerse{RevelationofJohn}{5}{12}\textsuperscript{,}\qVerse{RevelationofJohn}{13}{8}

Q. Should we then believe that the saints of old nourished themselves with Christ's Spirit, just as we do today?

A. The Church's forefathers were baptized unto Moses, and nourished themselves with the Spirit of Christ. [1 Cor. 10:1-4]\qRange{ICorinthians}{10}{1}{4}

Q. These Scriptures assert that Christ's death was meant to destroy and remit sin. Did He do this so that He no longer had work to do in us, and that we no longer had work to do for Him?

A. Christ suffered for us as an example, so that we could follow in His footsteps. [1 Pet. 2:21]\qVerse{IPeter}{2}{21}

Paul became a minister and was glad to suffer for Christ, for the sake of Christ's church. [Col. 1:23-24]\qRange{Colossians}{1}{23}{24}

Remember that Christ died so that His life could manifest through us. For we who live always risk death for Christ's sake, that His life is manifested through us. [2 Cor. 4:10-11]\qRange{IICorinthians}{4}{10}{11}

Christ died for everyone so that they would no longer live for themselves, but for the One who died for them and rose again. [2 Cor. 5:15]\qVerse{IICorinthians}{5}{15}

I will know him and the power of His resurrection, and share in his suffering, conforming to his death. [Phil. 3:10]\qVerse{Philippians}{3}{10}



	
	
	
	
	
	
	
	
	
\end{document}