%Section Template
\documentclass[../main.tex]{subfiles}

\begin{document}
	

	\section*{}
	Q. Where is God's love toward fallen and lost men?

	A. For God so loved the world, that he gave his only begotten Son, that whosoever believes in him should not perish, but have everlasting life. [John 3:16]\qVerse{John}{3}{16}

	God's love manifested in this: That God sent his only begotten Son into the world so we could live through him. [1 John 4:9]\qVerse{IJohn}{4}{9}

	Q. What does the Bible mean by "World"? Every man, or only a few?

	A. Jesus, who was made a little lower than the angels in order to die with glory and honor, tasted death for every man, by the grace of God. [Hebrews 2:9]\qVerse{Hebrews}{2}{9}

	If a man sins, he has an advocate with God in Jesus Christ, the righteous one; and he is the atonement for our sins, and not just ours, but the sins of the whole world. [1 John 2:1-2]\qRange{IJohn}{2}{1}{2}

	Q. It seems the apostle John is speaking plainly by mentioning the whole world. This must not only include the saints, but everyone else, since he clearly distinguishes the world from himself and all the saints he was writing to. What does Paul say about this?

	A. Christ within you is the hope of glory, and we preach of him, warning and teaching every man, so we that every man can be made perfect in Christ. [Colossians 1:27-28]\qRange{Colossians}{1}{27}{28}

	I strongly recommend that, first of all, supplications, prayers, intercessions, and giving of thanks be made for all men; for this is good and acceptable in the sight of God our Savior, who wishes all men would come to the knowledge of the truth; who gave himself as a ransom for all, to be testified in due time. [1 Timothy 2:1,3-6]\qVerse{ITimothy}{2}{1}\textsuperscript{,}\qRange{ITimothy}{2}{3}{6}

	Q. And what does the apostle Peter say about this?

	A. Tell them that God says, "I have no pleasure in the death of the wicked, but wish that the wicked would turn from their way and live." [Ezekiel 33:11]\qVerse{Ezekiel}{33}{11}

	God is gracious and compassionate; he is slow to anger, and very merciful. God is good to all, and His tender mercy is shown in His works. [Psalms 145:8-9]\qRange{Psalms}{145}{8}{9}

	In Christ, God reconciled the world to himself, not counting their sins against them. [2 Corinthians 5:19]\qVerse{IICorinthians}{5}{19}

	Q. These Scriptures seem to assert that God's love is offered to all, so that everyone could be saved by Christ. What, then, can be said about those who claim that God and Christ intended many men should never be saved; and that Christ's life and death were never intended for these men's justification, but rather would serve to condemn them, as God so desired, withholding salvation from the moment they were born?  What does Scripture say about this?

	A. God didn't send his son into the world to condemn the world, but so that through Him the world could be saved. [John 3:17]\qVerse{John}{3}{17}

	I come as a light into the world, that whoever believes in me doesn't abide in darkeness. If any man hears my words and doesn't believe him, I don't judge him for that, because I didn't come to judge the world, but to save it. [John 12:46-47]\qRange{John}{12}{46}{47}

	Q. Then what Scripture led such men to believe so wrongly?

	A. Before Jacob and Esau were even born, before they had done good or evil, in order that God's purpose in election could stand, not by their works but by God's will, Rebekah was told, "The older child will serve the younger, because I love Jacob and hate Esau." [Romans 9:11-13]\qRange{Romans}{9}{11}{13}

	Q. But the referenced Scripture only says that before the children were born, the older would serve the younger. The part about loving Jacob and hating Esau is taken from Malachi, who wrote them centuries after Jacob and Esau had died. Doesn't Scripture mention any other reason God hated Esau besides his own will? What does Paul say about this elsewhere in Scripture?

	A. No one should be immoral like Esau, who sold his birthright for a meal, since as a result, when he would have inherited the blessing, he was instead rejected. [Hebrews 12:16-17]\qRange{Hebrews}{12}{16}{17}

	Q. These men allege that Adam's sin damned many people, even children. But doesn't Scripture say that Christ's death could heal just as much as Adam's sin could damn?

	A. If one man's sin could damn many, God's grace through Jesus Christ could do so much more. By one man's sin, all were condemned, but by one man's righteousness, God gave everyone the chance to be justified. [Romans 5:15-19]\qRange{Romans}{5}{15}{19}

	Q. The proves that Christ's death can make up for Adam's sin. Why, then, are some still condemned?

	A. He who believes in Christ is not condemned, but he who doesn't believe is already condemned, because he hasn't believed in the name of the only begotten Son of God. [John 3:18]\qVerse{John}{3}{18}

	There are those unrighteous who will die, becuase they haven't received God's truth to be saved. For this, God will delude them with a lie, that those who didn't believe the truth but took pleasure in evil will be damned. [2 Thess. 2:10-12]\qRange{IIThessalonians}{2}{10}{12}

	Q. Seeing that Scripture testifies that God intended love and mercy for all through Christ, is the Gospel intended for everyone, in that they are able to receive God's grace?

	A. Continue in grounded faith, and don't be pulled away from the hope of the Gospel you've heard, which was preached to every creature, and of which I, Paul, am a minister. [Colossians 1:23]\qVerse{Colossians}{1}{23}

	Q. What is the Gospel?

	A. I'm not ashamed of the Gospel, for it is God's power of salvatoin for everyone who believes it. [Romans 1:16]\qVerse{Romans}{1}{16}

	Q. Is this Gospel hidden?

	A. If our Gospel is hidden, it is hidden to those who are lost, whose unbelieving minds God has blinded so that the light of this glorious Gospel would not shine on them. [2 Cor. 4:3-4]\qRange{IICorinthians}{4}{3}{4}

	Q. But hasn't this light come into the world? And aren't men condemned because they hate the light, not because it is hidden from them?

	A. The condemnation is this: Light has come into the world, but men prefer darkness. [John 3:19]\qVerse{John}{3}{19}

	Q. Why do they love darkness?

	A. They love darkness because their deeds are evil. [John 3:19]\qVerse{John}{3}{19}

	Q. Is every man given light by this light?

	A. John the Baptist was not the light, but was sent to bear witness of the true light which gives light to everyone in the world. [John 1:8-9]\qRange{John}{1}{8}{9}

	Q. Does this light discover everything?

	A. Everything the light shines on is made visible, and everything it shines on becomes a light. [Eph. 5:13]\qVerse{Ephesians}{5}{13}

	Q. Do evil men preach up this light, or care for it?

	A. Everyone who does evil hates the light, and they do not come to the light, or else their evil deeds would be discovered. [John 3:20]\qVerse{John}{3}{20}

	Q. Do good men love and follow the light?

	A. Whoever does what is true comes to the light, so that people can see their deeds are done in God. [John 3:21]\qVerse{John}{3}{21}

	Q. What does the light do for those love it and walk in it?

	A. If we walk in the light, we have fellowship with each other, and the blood of Jesus Christ, God's Son, cleanses us from all sin. [1 John 1:7]\qVerse{IJohn}{1}{7}

	Q. Does Christ command us to heed the light?

	A. While you have the light, believe in the light, so you can be children of the light. [John 12:36]\qVerse{John}{12}{36}

	Q. Were the apostles commanded to turn people toward the light?

	A. I am saving you (Paul) from your own people and the Gentiles.  I'm sending you to them to open their eyes and turn them away from darkness and toward the light, and from Satan toward God, so they can receive forgiveness of sins and join the sanctified through faith in Me. [Acts 26:17-18]\qRange{Acts}{26}{17}{18}

	Q. Does the light abide with everyone their whole lives, in order to save them, or only when God offers them His grace?

	A. The light is with you for a little while longer. Walk while you have the light, or darkness will overtake you. [John 12:35]\qVerse{John}{12}{35}

	Again, God set a certain day, telling David, "today". It is said, "Today, if you hear His voice, don't harden your hearts." [Hebrews 4:7]\qVerse{Hebrews}{4}{7}

	Q. How can it be proven that one day people may understand what will bring them peace, but afterwards it may be hidden from them?

	A. When he came near, he saw the city and wept for it, saying, "If you, even you, had only known today the things that give you peace; but now they are hidden from your eyes." [Luke 19:41-42]\qRange{Luke}{19}{41}{42}

	Q. What other Scriptures prove the Lord's willingness to gather a people who then rejected him and were condemned?

	A. Oh Jerusalem, Jerusalem, you who kills the prophets, and stones those who God sends you, how often I would have gathered your children together like a hen gathers her chicks under her wings, but you refused! [Matthew 23:37]\qVerse{Matthew}{23}{37}

	The the servant's lord said, "You wicked servant! I forgave all your debts because you asked me; shouldn't you have had mercy for your fellow servant, just like I had pity on you? His lord was furiour and gave the servant over to his tormentors until he paid all he owed. [Matt. 23:37; Luke 13:34]\qVerse{Matthew}{23}{37}\textsuperscript{,}\qVerse{Luke}{13}{34}

	Then Paul and Barnabas boldly said, "It was necessary to preach the word of God to you, but seeing you've rejected it, judging yourselves unworthy of everlasting life, we'll turn to the Gentiles instead." [Acts 13:46]\qVerse{Acts}{13}{46}

	Because I called and you refused, because I offered my hand and no one took it, because you ignored my commands and rejected my rebukes, I will laugh at your destruction and mock your fear. [Proverbs 1:24-26]\qRange{Proverbs}{1}{24}{26}

	I will speak of a nation, and of the kingdom that will build and plant it: If it does evil by not obeying me, I will withhold the good I intended for it. [Jeremiah 18:9-10]\qRange{Jeremiah}{18}{9}{10}

	Q. Does God's Spirit stay for a while, and then afterwards leave?

	A. And the Lord said, "My Spirit will not always be with people." [Genesis 6:3]\qVerse{Genesis}{6}{3}

	Q. Can the Spirit be resisted?

	A. You stubborn and unsaved people, you always resist the Holy Spirit, just like your fathers did. [Acts 7:51]\qVerse{Acts}{7}{51}

	God's wrath is revealed from heaven against the evils of man, who hide the truth in evil. [Romans 1:18]\qVerse{Romans}{1}{18}

	Q. Is this light given to evil people?

	A. Jesus told them many things through parables: "A farmer went our to plant his seeds, and when he planted, some seeds fell in the wrong place, and some among stones, and some among thorns. [Matt. 13:3-7]\qRange{Matthew}{13}{3}{7}

	Q. Are these places where the seeds are said to have fallen a metaphor for men's hearts?

	A. This is the meaning of the parable: When someone hears God's word and doesn't understand it, the the wicked one comes and takes away what was planted in his heart. This is what I mean by seeds falling by the wayside. [Matt. 13:18-19]\qRange{Matthew}{13}{18}{19}

	Q. Is this seed small at first sight?

	A. The Kingdom of Heaven is like a mustard seed, the smallest of all seeds, planted in a field. [Matt. 13:31-32]\qRange{Matthew}{13}{31}{32}

	Q. For those who don't understand these metaphors (even though they're in the Bible): Does God offer His Spirit to everyone?

	A. The Spirit is given to everyone, for their benefit. [1 Cor. 12:7]\qVerse{ICorinthians}{12}{7}

	Q. If it is for their benefit, then is must be for their salvation. Otherwise, how could it benefit them at all? But regarding those who distinguish a "common" grace from a saving grace, is saving grace offered to all?

	A. God's saving grace has appeared to all men. [Titus 2:11]\qVerse{Titus}{2}{11}

	Q. Anything that gives salvation must be saving grace. But what does this saving grace teach us?

	A. Teaching us to deny ungodliness and worldly desires and instead life righteously, godly, and soberly in this present world. [Titus 2:12]\qVerse{Titus}{2}{12}

	Q. Whatever teaches righteousness and godliness but be sufficient to save, because therein is the entire duty of man.  What does Paul say elsewhere about this teacher?

	A. Now, brothers, I urge you to turn to God, and to His grace, which can build you up and number you among the saints. [Acts 20:32]\qVerse{Acts}{20}{32}

	Q. What is God's word?

	A. God's word is quick and powerful, sharper than any two-edged sword, sharp enough to cleave the soul and spirit from the body. It knows the thoughts and the heart. Nothing is hidden from it, but everything is naked and open to the eyes of Him to whom we must be accountable. [Hebrews 4:12-13]\qRange{Hebrews}{4}{12}{13}

	Q. Should we obey this word?

	A. We have a more sure prophecy, to which you should take heed, like a light shining in a dark place, until the day dawns and the sun rises in your hearts. [2 Peter 1:19]\qVerse{IIPeter}{1}{19}

	Q. I see the Scriptures are very clear about the universality and sufficiency of this light, seed, grace, and word of God, but is the word with us or far way, is it inward, or outward?

	A. Don't say in your heart, "Who will go to heaven to bring Christ down here?" or "Who will go down to the depths to bring Christ up from the dead?  The word we preach sais that the word is near you, in your mouth and you heart. [Romans 10:6-8]\qRange{Romans}{10}{6}{8}

	Q. That's clear about the word, but what about the light being inward?

	A. God, who commanded light to shine out of darkness, has shined in our hearts, to give the light of the knowledge of the glory of God in the face of Jesus Christ. We have this light in our earthly bodies, so that the power is of God, not of us. [2 Cor. 4:6-7]\qRange{IICorinthians}{4}{6}{7}

	Q. Since it's also called the seed of the kingdom, does that mean God's kingdom is within us?

	A. God's Kingdom is not seen with the eachs, but rather it is within you. [Luke 17:20-21]\qRange{Luke}{17}{20}{21}








\end{document}